\documentclass[11pt]{article}
\usepackage{fullpage, fancyhdr, ifthen, amssymb, amsfonts, amsmath, booktabs}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[margin=0.25in]{geometry}
\usepackage{forest}
\usepackage{textcomp}
\usepackage{upquote}
\usepackage{colortbl}


\begin{document}
\begin{tabularx}{\textwidth}{l|X}
\textbf{Quiz 6A} &   \textbf{Name: } \\
\hline
\end{tabularx}


\noindent \textbf{Instructions:} Please answer the following questions making sure to write your answers legibly. The code below contains routes from a Flask app.
\begin{itemize}
\item Since we are writing python code please be careful about spacing / indent. Leave enough room that it is obvious when you want things indented. 
\item Make sure to write legibly.

\end{itemize}


{\color{lightgray}\hrule}
\begin{verbatim}

@app.route( '/api/question2/<int:base>/<int:power>', methods=['GET'])
def calculate_power(base, power):
    # Question #2
    final_result = {'result': base ** power}
    return jsonify(final_result), 200

@app.route('/api/question3/count/<string:text_input>', methods=['GET'])
def count_characters(text_input):
    # Question #3
\end{verbatim}
{\color{lightgray}\hrule}

\vspace{.5cm}

\begin{enumerate}
\item (8 Points) Fill in the table below showing what CRUD operations stand for and their corresponding HTTP methods. 


\begin{center}
	

\begin{tabular}{|c|p{8cm}|p{6cm}|}
\hline 
Letter & \centering What it stands for &  HTTP Method Used \\
\hline
C & & \\[1cm]
\hline
R & & \\[1cm]
\hline
U & & \\[1cm]
\hline
D & & \\[1cm]
\hline
\end{tabular}

\end{center}

\item (6 Points) Using the code above what will the following GET requests return?
\subitem (a) GET: /api/question2/2/3
\vspace{1cm}
\subitem (b) GET: /api/question2/4/2

\vspace{1cm}

\item (5 Points) The 2nd route above counts the number of characters in a string. If a GET request is sent to \newline \texttt{/api/question3/count/nickross} it should return \texttt{\{ \textquotesingle length\textquotesingle  : 8\}}, where 8 is the number of characters in \texttt{nickross}. Please complete the function in the space below. You need not repeat the code already written above (or you can).

\end{enumerate}


\end{document}